The Name of the Title is Hope

### 2020-03-19 intro.tex
We have a methods section

Our work is based on\textsc{Hoogle+}, a program synthesis engine for the
Haskell programming language \cite{hoogle_plus_2020}.
%
A user inputs a type signature of a function, like \texttt{a -> [Maybe a] -> a}
(read: ``A function that takes a thing and a list of optional-things, and
returns a thing'').
%
\textsc{Hoogle+} then looks for Haskell programs that use library calls (from
a small, builtin set of functions) that satisfies the type signature.
%
Note that there may be an infinite number of so-called \emph{inhabitants} of a type.
%
This presents a search problem for users of the system.

>>>>

Our work is based on \hoogleplus, a program synthesis engine for the
Haskell programming language \cite{hoogle_plus_2020}.
%
A user inputs a type signature of a function, like \texttt{a -> [Maybe a] -> a}
(read: ``A function that takes a thing and a list of optional-things, and
returns a thing'').
%
\hoogleplus then looks for Haskell programs that use library calls (from
a small, builtin set of functions) that satisfies the type signature.
%
Note that there may be an infinite number of so-called \emph{inhabitants} of a type.
%
This presents a search problem for users of the system.

### 2020-03-19 methods.tex
We have a methods section

\section{Method}

% --- COPIED FROM ABSTRACT ASSIGNMENT --- %
% Explain your study design, illustrate how the study's results will provide
% evidence for/against your hypothesis, and how the question, hypothesis, and
% study all line up. We encourage you to mirror/copy/adapt other researchers
% methods (e.g. by drawing from the class readings) whenever appropriate (and
% not when it isn't appropriate).

% There are three major points you should hit here.

% Study design:
% What are you going to do? Be detailed and precise.

% Ecological Validity:
% Why does your study answer your research question? Why
% does your evaluation address your hypothesis? Make sure your study, and the
% variables you're measuring, properly address the question you are asking.
\subsection{Measures}
For each participant, we measured:
\begin{itemize}
    \item Time-to-correct solution (per task)
    \item Count of incorrect guesses (per task)
    \item Count and type of interpreter queries (across all tasks)
\end{itemize}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{method/control-ui.png}
        \caption{Control treatment, no examples}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{method/treatment-ui.png}
        \caption{Experimental treatment, examples}
    \end{subfigure}
    \caption{Each participant received one of the two treatments for the duration of the study.}
\end{figure*}

>>>>

\section{Method}
\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{method/control-ui.png}
        \caption{Control treatment, no examples}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{method/treatment-ui.png}
        \caption{Experimental treatment, examples}
    \end{subfigure}
    \caption{Each participant received one of the two treatments for the duration of the study.}
    \label{fig:ui}
\end{figure*}
To assess whether examples aid recognition of candidate programs, we
developed two variants of a synthesizer interface (see Figure~\ref{fig:ui})

\paragraph{No-examples variant}
%
In the \noexamples variant, a user can enter a Haskell type signature at the top and get a
list of 10 candidate programs back.
%
These candidates are unmodified and in the same order that \hoogleplus
synthesizer generates them.
%
The results are deterministic meaning that for a given type signature, the
response is always the same.

\paragraph{Examples variant}
The \examples variant extends the \noexamples variant with input/output
examples for each candidate.
%
For each, type signature in the study, we manually created three simple
inputs of the appropriate type.
%
Each candidate program received the same three inputs.

\subsection{Procedure}
We gathered 10 haskell-literate participants from around our department's
building and from the local Hillcrest community.
%
Participants were each assigned to either the \noexamples treatment or the
\examples treatment for the duration of the study.
%
Each participant was presented a laptop with their respective tool variant open
and an interactive haskell interpreter (GHCI) open to the side.
%
Throughout the study participants were allowed to use only the tool and the
interpreter.

After a brief tutorial tasks, participants were asked to complete 4 tasks.
%
Each task consisted of a type signature they would enter, and an informal
english description of the behavior they were looking for.
%
They would then enter the type signature and identify the candidate program that
met the specification, if it was present.
%
Participants were told at the beginning that the solution may not be present
in the list---Task 3 did not have a solution in the list.

After completing the four tasks, the candidates were given a brief survey
that asked them about their haskell experience, their opinions on the tool,
and their strategies for finding the correct answer.

\subsection{Measures}

For each participant, we measured:
\begin{itemize}
    \item Time-to-correct solution (per task)
    \item Count of incorrect selections (per task)
    \item Count and type of interpreter queries (across all tasks)
\end{itemize}

@@
